Temporal Dynamics of Normalization Reweighting

### 2022-10-02 manuscript.Rmd
Bug fixes

processdata <- 0  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data (requires XGB of storage)
# 2 - download processed individual data and analyse (requires XGB of storage)
# 3 - download all raw data and analyse (requires 78+GB of storage)

@@

# check if directories exist to store data files (ignored by git)
if (!dir.exists('temp/')){dir.create('temp/')}
if (!dir.exists('temp/VilidaiteProcessed/')){dir.create('temp/VilidaiteProcessed/')}
if (!dir.exists('temp/raw/')){dir.create('temp/raw/')}
if (!dir.exists('temp/raw/temp/')){dir.create('temp/raw/temp/')}
if (!dir.exists('temp/MEGdata/')){dir.create('temp/MEGdata/')}
if (!dir.exists('temp/EEGprocessed/')){dir.create('temp/EEGprocessed/')}
if (!dir.exists('temp/pilotraw/')){dir.create('temp/pilotraw/')}
if (!dir.exists('temp/pilotraw/temp/')){dir.create('temp/pilotraw/temp/')}

@@

osfproject <- osf_retrieve_node("ab3yv")
componentlist <- osf_ls_nodes(osfproject)
osffiles <- osf_ls_files(osfproject,n_max=300)

pilotproject <- osf_retrieve_node("y4n5k")
pilotfiles <- osf_ls_files(pilotproject,n_max=300)
if (!file.exists('temp/headerfile.csv')){
  hid <- pmatch('headerfile.csv',as.character(unlist(pilotfiles[,1])))
  osf_download(pilotfiles[hid,], path='temp/')
}
hdata <- read.csv('temp/headerfile.csv')

@@

    if (!file.exists(paste0(datadir,tarname))){
      fid <- which(pilotfiles$name==tarname)
      osf_download(pilotfiles[fid,],datadir,progress=TRUE)
    }
    untar(paste0(datadir,tarname),exdir=paste0(datadir,subname))
    file.remove(paste0(datadir,tarname))  # delete after unpacking

    condcounter <- (1:20) * 0
    allsamples <- array(0, dim = c(10,20,64,duration*samplerate))
    d <- dir(path = paste0(datadir,subname), pattern='*.csv.gz',full.names=TRUE)

    for (block in 1:length(d)) {
      EEGdata <- read.csv(d[block], header = TRUE)

@@

     # optionally delete the files after use
    # for (block in 1:length(d)){file.remove(d[block])}

  }
}
}
}

@@

# download any missing data files from osf
if (length(d)<100){
  pilotrepo <- pmatch('Processed pilot data',as.character(unlist(componentlist[,1])))
  pilotfiles <- osf_ls_files(componentlist[pilotrepo,2],n_max=300)
  for (s in 1:length(pilotfiles)){
    if (!file.exists(paste0('temp/VilidaiteProcessed/',pilotfiles[s,1]))){
      osf_download(pilotfiles[s,],'temp/VilidaiteProcessed/',progress=TRUE)
    }
  }
}

@@

Pilotpercentexcluded <- 100 - (100*mean(alltrialcounts[,condlist,28:31])/8)
targetcond <- NULL
maskcond <- NULL
subj <- NULL
targetamp <- NULL
maskamp <- NULL
i <- 0
for (s in 1:100){
  for (cond in 1:14){
    i <- i + 1
    subj[i] <- s
    targetcond[i] <- ((cond-1) %% 7) + 1
    maskcond[i] <- ceiling(cond/7)
    targetamp[i] <- abs(EEGallconds[s,1,cond])
    maskamp[i] <- abs(EEGallconds[s,2,cond])
  }
}
anovadata <- data.frame(subj,targetcond,maskcond,targetamp,maskamp)
anovadata$subj <- as.factor(anovadata$subj)
anovadata$targetcond <- as.factor(anovadata$targetcond)
anovadata$maskcond <- as.factor(anovadata$maskcond)

@@

subjcounter <- 0
for (datahalf in 1:length(EEGID)){
  EEGtoken <- componentlist[EEGID[datahalf],2]
  EEGfiles <- osf_ls_files(EEGtoken,n_max=300)
  for (f in 1:nrow(EEGfiles)){
    subjcounter <- subjcounter + 1
    print(subjcounter)
    # first check if we have this participant's data
    if (!file.exists(paste0('temp/EEGprocessed/S',subjcounter,'data.RData'))){
      # if we haven't processed the data, check if we need to download the raw data
      if (!dir.exists(paste0('temp/raw/S',subjcounter))){
        if (!file.exists(paste0('temp/raw/S',subjcounter,'.zip'))){
          osf_download(EEGfiles[f,], path='temp/raw/',progress=TRUE)
        }
          unzip(paste0('temp/raw/S',subjcounter,'.zip'),exdir='temp/raw/')
          file.remove(paste0('temp/raw/S',subjcounter,'.zip'))
      }
    # if necessary, process the data for this participant

      d <- dir(paste0('temp/raw/S',subjcounter), pattern='*.csv.gz',full.names=TRUE)
      condcounter <- (1:4) * 0
      alltrials <- array(0,dim=c(50,4,9000,64))
      subjwaves <- array(0,dim=c(4,9000,64))
      trialsincluded <- matrix(0,nrow=4,ncol=64)

@@

      qdatasubj <- read.csv(paste0('temp/raw/S',subjcounter,'/questionnairedata.csv'))
      save(file=paste0('temp/EEGprocessed/S',subjcounter,'data.RData'),list=c('qdatasubj','condcounter','trialsincluded','subjwaves','electrodes'))
    }
 }
}

@@

# download any missing data files from osf
if (length(d)<100){
  EEGrepo <- pmatch('Processed EEG data',as.character(unlist(componentlist[,1])))
  EEGfiles <- osf_ls_files(componentlist[EEGrepo,2],n_max=300)
  for (s in 1:length(EEGfiles)){
    if (!file.exists(paste0('temp/EEGProcessed/',EEGfiles[s,1]))){
      osf_download(EEGfiles[s,],'temp/EEGProcessed/',progress=TRUE)
    }
  }
}

@@

  # download any missing data files from osf
if (length(d)<20){
  MEGrepo <- pmatch('Processed MEG data',as.character(unlist(componentlist[,1])))
  MEGfiles <- osf_ls_files(componentlist[MEGrepo,2],n_max=300)
  for (s in 1:length(MEGfiles)){
    if (!file.exists(paste0('temp/MEGdata/',MEGfiles[s,1]))){
      osf_download(MEGfiles[s,],'temp/MEGdata/',progress=TRUE)
    }
  }
}

>>>>

processdata <- 0  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data (requires 0.4GB of storage)
# 2 - download processed individual data and analyse (requires 11.5GB of storage)
# 3 - download all raw data and analyse (requires 143GB of storage)

@@

# check if directories exist to store data files (ignored by git)
if (!dir.exists('temp/')){dir.create('temp/')}
if (!dir.exists('temp/VilidaiteProcessed/')){dir.create('temp/VilidaiteProcessed/')}
if (!dir.exists('temp/raw/')){dir.create('temp/raw/')}
if (!dir.exists('temp/raw/temp/')){dir.create('temp/raw/temp/')}
if (!dir.exists('temp/MEGdata/')){dir.create('temp/MEGdata/')}
if (!dir.exists('temp/EEGprocessed/')){dir.create('temp/EEGprocessed/')}
if (!dir.exists('temp/pilotraw/')){dir.create('temp/pilotraw/')}

@@

osfproject <- osf_retrieve_node("ab3yv")
componentlist <- osf_ls_nodes(osfproject)
osffiles <- osf_ls_files(osfproject,n_max=300)
pilotproject <- osf_retrieve_node("y4n5k")
pilotfiles <- osf_ls_files(pilotproject,n_max=300)

if (!file.exists('temp/headerfile.csv')){
  hid <- pmatch('headerfile.csv',as.character(unlist(pilotfiles[,1])))
  osf_download(pilotfiles[hid,], path='temp/')
}
hdata <- read.csv('temp/headerfile.csv')

@@

    if (!file.exists(paste0(datadir,tarname))){
      fid <- which(pilotfiles$name==tarname)
      if (!pracma::isempty(fid)){
      osf_download(pilotfiles[fid,],datadir,progress=TRUE)}
    }
    if (file.exists(paste0(datadir,tarname))){
    untar(paste0(datadir,tarname),exdir=paste0(datadir,subname))
    file.remove(paste0(datadir,tarname))  # delete after unpacking
    }
    condcounter <- (1:20) * 0
    allsamples <- array(0, dim = c(10,20,64,duration*samplerate))
    d <- dir(path = paste0(datadir,subname), pattern='*.csv.gz',full.names=TRUE)

    if (!pracma::isempty(d)){
    for (block in 1:length(d)) {
      EEGdata <- read.csv(d[block], header = TRUE)

@@

     # optionally delete the files after use
    # for (block in 1:length(d)){file.remove(d[block])}
}
  }
}
}
}

@@

# download any missing data files from osf
if (length(d)<100){
  pilotrepo <- pmatch('Processed pilot data',as.character(unlist(componentlist[,1])))
  pilotfiles <- osf_ls_files(componentlist[pilotrepo,2],n_max=300)
  for (s in 1:nrow(pilotfiles)){
    if (!file.exists(paste0('temp/VilidaiteProcessed/',pilotfiles[s,1]))){
      osf_download(pilotfiles[s,],'temp/VilidaiteProcessed/',progress=TRUE)
    }
  }
}

@@

Pilotpercentexcluded <- 100 - (100*mean(alltrialcounts[,condlist,28:31])/8)
targetcond <- NULL
maskcond <- NULL
subj <- NULL
targetamp <- NULL
maskamp <- NULL
i <- 0
for (s in 1:dim(EEGallconds)[1]){
  for (cond in 1:14){
    i <- i + 1
    subj[i] <- s
    targetcond[i] <- ((cond-1) %% 7) + 1
    maskcond[i] <- ceiling(cond/7)
    targetamp[i] <- abs(EEGallconds[s,1,cond])
    maskamp[i] <- abs(EEGallconds[s,2,cond])
  }
}
anovadata <- data.frame(subj,targetcond,maskcond,targetamp,maskamp)
anovadata$subj <- as.factor(anovadata$subj)
anovadata$targetcond <- as.factor(anovadata$targetcond)
anovadata$maskcond <- as.factor(anovadata$maskcond)

@@

subjcounter <- 0
for (datahalf in 1:length(EEGID)){
  EEGtoken <- componentlist[EEGID[datahalf],2]
  EEGfiles <- osf_ls_files(EEGtoken,n_max=300)
  for (f in 1:nrow(EEGfiles)){
    subjcounter <- subjcounter + 1
    subID <- unlist(strsplit(EEGfiles$name[f],'.zip'))
    print(subID)
    # first check if we have this participant's data
    if (!file.exists(paste0('temp/EEGprocessed/',subID,'data.RData'))){
      # if we haven't processed the data, check if we need to download the raw data
      if (!dir.exists(paste0('temp/raw/',subID))){
        if (!file.exists(paste0('temp/raw/',EEGfiles$name[f]))){
          osf_download(EEGfiles[f,], path='temp/raw/',progress=TRUE)
        }
          unzip(paste0('temp/raw/',EEGfiles$name[f]),exdir='temp/raw/')
          file.remove(paste0('temp/raw/',EEGfiles$name[f]))
      }
    # if necessary, process the data for this participant

      d <- dir(paste0('temp/raw/',subID), pattern='*.csv.gz',full.names=TRUE)
      condcounter <- (1:4) * 0
      alltrials <- array(0,dim=c(50,4,9000,64))
      subjwaves <- array(0,dim=c(4,9000,64))
      trialsincluded <- matrix(0,nrow=4,ncol=64)

@@

      qdatasubj <- read.csv(paste0('temp/raw/',subID,'/questionnairedata.csv'))
      save(file=paste0('temp/EEGprocessed/',subID,'data.RData'),list=c('qdatasubj','condcounter','trialsincluded','subjwaves','electrodes'))
    }
 }
}

@@

# download any missing data files from osf
if (length(d)<100){
  EEGrepo <- pmatch('Processed EEG data',as.character(unlist(componentlist[,1])))
  EEGfiles <- osf_ls_files(componentlist[EEGrepo,2],n_max=300)
  for (s in 1:nrow(EEGfiles)){
    if (!file.exists(paste0('temp/EEGprocessed/',EEGfiles[s,1]))){
      osf_download(EEGfiles[s,],'temp/EEGprocessed/',progress=TRUE)
    }
  }
}

@@

  # download any missing data files from osf
if (length(d)<20){
  MEGrepo <- pmatch('Processed MEG data',as.character(unlist(componentlist[,1])))
  MEGfiles <- osf_ls_files(componentlist[MEGrepo,2],n_max=300)
  for (s in 1:nrow(MEGfiles)){
    if (!file.exists(paste0('temp/MEGdata/',MEGfiles[s,1]))){
      osf_download(MEGfiles[s,],'temp/MEGdata/',progress=TRUE)
    }
  }
}
